Stack Overflow Comparison

### 2017-08-10 functions.Rmd
updated hours, organized files

```{r}
#function to import and set up the data 
setup <- function() {
  dir <- file.path(getwd(),"data")
  out <- read.csv(file.path(dir, "answers_data.csv"))

  library(dplyr)
  x <- out %>% 
    tbl_df() %>%
    filter(langid == "en")

  x$time_until_answer <- (x$first_answer_date - x$post_date)/3600
  empty <- which(is.na(x$time_until_answer))
  for (i in empty) {
    x$time_until_answer[i] <- (x$download_date[i] - x$post_date[i])/3600
}
}
```

@@

#function to plot survfit objects
#input: survfit object, data, optional x-axis limits
plot_surv <- function(survfit, data, xlim = NULL) {
  library(ggfortify)
  library(directlabels)

@@

#function that prints out summary stats grouped by that variable 
sum_stats <- function(variable, data) {
  tbl <- x %>%
    group_by(data[[variable]]) %>%
    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
    arrange(median_time)
  names(tbl)[1] <- variable
  return(tbl)
}
```

@@

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)

@@

#function to calculate r-square adjusted
#k = number of independent predictors 
get_rsq_adj <- function(cr_obj, k) {
  r <- unname(summary(cr_obj)$rsq[1])
  n <- summary(cr_obj)$n
  radj <- 1- (((1- (r**2)) * (n - 1))/(n-k-1))
  return(radj)
}

#add in function to compare nested models

>>>>

```{r}
#function to import and set up the data 
oshitar::setup()
```

@@

#function to plot survfit objects
#input: survfit object, data, optional x-axis limits
get_survplot <- function(survfit, data, xlim = NULL) {
  library(ggfortify)
  library(directlabels)

@@

#function that prints out summary stats grouped by that variable 
get_summaries <- function(variable, data) {
  tbl <- x %>%
    group_by(data[[variable]]) %>%
    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
    arrange(median_time)
  names(tbl)[1] <- variable
  return(tbl)
}
```

@@

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n and stopwrds are an optional arguments
get_freq_terms <- function(vec, n = NULL, stopwrds = NULL) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)

@@

#function to calculate r-square adjusted
#k = number of independent predictors 
get_rsq_adj <- function(cox, k) {
  r <- unname(summary(cox)$rsq[1])
  n <- summary(cox)$n
  radj <- 1 - (((1 - (r**2)) * (n - 1))/(n-k-1))
  return(radj)
}

#function to compare nested models
#full and reduced = number of parameters 
compare_nested <- function(crfull, crreduced) {
  loglik_f <- summary(crfull)[["loglik"]][2]
  loglik_r <- summary(crreduced)[["loglik"]][2]
  stat <- 2*(loglik_f - loglik_r)

  full <- length(crfull[["coefficients"]])
  reduced <- length(crreduced[["coefficients"]])

  df <- full - reduced
  pval <- 1 - pchisq(stat, df)
  results <- data.frame(statistic = stat, pval = pval)
  return(results)
}

### 2017-08-10 model fitting/model_fitting.Rmd
updated hours, organized files

#length of sentence till first punctuation mark 
x$text_till_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]
x$text_till_punct[is.na(x$text_till_punct)] <- 5000

@@

@@

```{r}
#function to compare nested models
#full and reduced = number of parameters 
compare_nested <- function(crfull, crreduced, full, reduced) {
  s_full <- summary(crfull)
  s_red <- summary(crreduced)
  like_f <- s_full[[loglik]]
  like_r <- s_red[[loglik]]
  stat <- 2*(like_f - like_r)
  df <- param_full - param_reduced
  pval <- 1 - pchisq(stat, df)
  return(stat, pval)
}

@@

#not calling loglik 
compare_nested("cr11", "cr11_r", full = 18, reduced = 17)

@@

>>>>

#length of sentence till first punctuation mark 
x$text_till_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]
x$text_till_punct[is.na(x$text_till_punct)] <- 5000
#categorize this- zero, small, short, long...

@@

```{r}
ggplot(x, aes(x = time_until_answer, y = avg_tag_score, color = as.factor(answered))) + 
  geom_point()

library(ggplot2)
```

@@

```{r}
#function to compare nested models
#full and reduced = number of parameters 
compare_nested <- function(crfull, crreduced) {
  loglik_f <- summary(crfull)[["loglik"]][2]
  loglik_r <- summary(crreduced)[["loglik"]][2]
  stat <- 2*(loglik_f - loglik_r)

  full <- length(crfull[["coefficients"]])
  reduced <- length(crreduced[["coefficients"]])

  df <- full - reduced
  pval <- 1 - pchisq(stat, df)
  results <- data.frame(statistic = stat, pval = pval)
  return(results)
}

#full
cr11 <- coxph(Surv(time_until_answer, answered) ~ category + 
                 device_length + n_images + new_user + post_weekday + 
                 post_ampm + contain_unanswered + contain_answered + avg_tag_score + 
                 title_questionmark + title_begin_wh + capital_text + 
                 capital_title + text_all_lower + prior_effort + update + 
                 newline_ratio + title_questionmark*title_begin_wh, data = x)

@@

compare_nested(cr11, cr11_r)
```

@@

```{r}
cr14 <- coxph(Surv(time_until_answer, answered) ~ avg_tag_score, data = x)
summary(cr14)
names(cr14)
length(cr14$coefficients)
```

### 2017-08-10 model fitting/stackoverflow_comparison.Rmd
updated hours, organized files

```{r, echo = FALSE}
#using cut function to divide range of title lengths into intervals 
x$title_ints <- cut(x$title_length, breaks = 5)

get_boxplot("title_ints", xaxis = "Intervals of title length (characters)", title = "title_ints")
```

>>>>

```{r, echo = FALSE}
#using cut function to divide range of title lengths into intervals 
x$title_ints <- cut(x$title_length, breaks = 5)
table(x$title_ints)

get_boxplot("title_ints", xaxis = "Intervals of title length (characters)", title = "title_ints")

cr5 <- coxph(Surv(time_until_answer, answered) ~ title_ints, data = x)
summary(cr5)
```
